\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 abstract.tex
.

Models of embedded control systems are often so complex that
falsification and testing approaches can scale only by numerically
simulating them, and hence treating the systems as black-boxes. Common
approaches like sampling-based falsification, use numerical
simulations to search for violations of safety properties. However,
this relegates them to the `best effort' category. On the other hand,
\emph{rigorous} verification (and falsification) techniques require
symbolic models and are comparatively less scalable. We try to bridge
this gap by incorporating data-driven models in a sampling based
search. Using an efficient, on-the-fly discrete abstraction
search procedure, we compute models only for selective regions of the state
space, thus `enriching' the abstraction. We then show how the
`enriched' abstraction can be used to guide the search for violations
without refinement.
%We use grid-based discrete abstractions to partition
%the state-space of the black-box hybrid dynamical system. We then use
%an efficient search procedure to find abstract violations of safety
%properties
%Assuming a grid-based implicit abstraction over the
%state-space of the black-box hybrid dynamical system, we enumerate
%abstract violations of the safety property. We then model the system
%behavior along these violations and search for concrete violations.
The automatic falsification proceeds by (a) randomly exploring the
state-space abstraction using numerically computed trajectories and
enumerating abstract violations, (b) modeling the behavior of the
system along these abstract violations by using discrete-time
piecewise affine (PWA) \emph{relational} models, and finally, (c)
encoding the search for a concrete violation as a bounded model
checking (BMC) problem.  The BMC query is then a disjunction of
conjunctions of linear constraints (i.e. combinations of linear
programs). It can be solved using off-the-shelf SMT solvers or by
multiple runs of a linear programming solver. For any counter-example
found in this `enriched' abstraction, we check the existence of a
corresponding violation in the original system. We demonstrate the
efficacy of our technique on a few benchmarks.

>>>>

Models of embedded control systems are often so complex that
falsification and testing approaches can scale only by numerically
simulating them, and hence treat the systems as black-boxes. Common
approaches like sampling-based falsification use numerical simulations
to search for violations of safety properties. However, this relegates
them to the `best effort' category. On the other hand, \emph{rigorous}
verification (and falsification) techniques require symbolic models
and are comparatively less scalable. We try to bridge this gap by
incorporating data-driven models in a sampling based search. Using an
efficient, on-the-fly discrete abstraction search procedure and
regression, we selectively model the behavior of the system in
sub-regions of the state space. We then incorporate the model in the
discrete abstractio, thus, `enriching' the abstraction. We show how
this `enriched' abstraction can be used to guide the search for
violations without refinement.  The automatic falsification proceeds
by (a) randomly exploring the state-space abstraction using
numerically computed trajectories and enumerating abstract violations,
(b) modeling the behavior of the system along these abstract
violations by using discrete-time piecewise \emph{relational} models,
and finally, (c) encoding the search for a concrete violation as a
bounded model checking (BMC) problem.  The BMC query is a disjunction
of conjunctions of constraints (i.e. a combination of constraint
problems over real arithmetic). It can be solved using off-the-shelf
SMT solvers or by multiple runs of an optimization solver (which
checks feasibility). For any counter-example found in this `enriched'
abstraction, we check the existence of a corresponding violation in
the original system. We demonstrate the technique on a few benchmarks.

%We use grid-based discrete abstractions to partition
%the state-space of the black-box hybrid dynamical system. We then use
%an efficient search procedure to find abstract violations of safety
%properties
%Assuming a grid-based implicit abstraction over the
%state-space of the black-box hybrid dynamical system, we enumerate
%abstract violations of the safety property. We then model the system
%behavior along these violations and search for concrete violations.
